Guarded Recursion in Agda via Sized Types

### 2019-02-04 code-oneclock-paper/latex/paper.tex
Definitional equality in different paragraph
Different version of conclusion

\subsection{Modelling Simple Types}
\label{sec:kripke}
\input{CloTT/Structure/Contexts}
\input{CloTT/Structure/Types}
\input{CloTT/Structure/Terms}
\input{CloTT/Structure/Subst}
\input{CloTT/Structure/DefinitionalEquality}

@@

Finally, we want to understand whether it is possible to reduce sized
types to guarded recursion.  This does not seems directly doable,
since sizes are not uniquely employed with coinductive types as a tool
for easing the productivity check of corecursive definitions, but they
are also used as auxiliary arguments of inductive types for
facilitating the termination check of recursive definitions. It seems
that, in order to capture this dual aspect of sizes, one needs to
extend the existing type theories for guarded recursion with
additional features.
%%
%% Bibliography
%%

>>>>

\subsection{Modelling Simple Types}
\label{sec:kripke}
\input{CloTT/Structure/Contexts}
\input{CloTT/Structure/Types}
\input{CloTT/Structure/Terms}
\input{CloTT/Structure/Subst}
%\input{CloTT/Structure/DefinitionalEquality}

@@

\remove{
Finally, we want to understand whether it is possible to reduce sized
types to guarded recursion.  This does not seems directly doable,
since sizes are not uniquely employed with coinductive types as a tool
for easing the productivity check of corecursive definitions, but they
are also used as auxiliary arguments of inductive types for
facilitating the termination check of recursive definitions. It seems
that, in order to capture this dual aspect of sizes, one needs to
extend the existing type theories for guarded recursion with
additional features.
}

Finally, we would like to understand whether sized types can be simulated using guarded recursion.
The difficulty is representing coinductive types.
One could represent sizes by the conatural numbers, but this might not be sufficient to model infinitary coinductive types.
%%
%% Bibliography
%%
